---
title: "About Models"
author: "Ryu Pape"
date: "5/17/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(neuralnet)
library(caret)
```


## Data wrangling/pre-processing
Only applies to OHIE dataset
```{r load file and models for reporting, include=FALSE}
load("nn2.Rdata")
load("nn4.Rdata")
```
## Slide with Bullets

- Insurance.csv
  - Multiple Linear Regression
- OHIE
  - Multiple Linear Regression
  - Simple Tree Regression
  - Random Forest Regression
  - Gradient boosting Regression(best performing)
  - Artificial Neural Networks Regression

# insurance.csv
Insurance

## Underlying Algorithm behind predictions
Mutliple Linear Regression
```{r cars, echo = TRUE}

```
# OHIE_Final_Selection.RDS

## Multiple Linear Regression

```{r pressure}

```

## Simple Tree Regression
```{}
## Random Forest Regression

## Gradient boosting Regression

## Artificial Neural Network Regression
Tried out many different parameters with different levels of complexity.
A Neural Network with 1 Hidden Layer and 1 Neuron, using a softplus activation function.
```{r nn1 Neural Networks presentation}

plot(nn2, rep = "best")
plot(nn4, rep = "best")
```